Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Revising Chapter 6

@@

Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fuleed burner in the corner position with walls of open back construction.

@@

	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner.}
	\label{Gas_Corner}
\end{figure}

@@

>>>>

Table~\ref{tab:Fire_Pattern_Dimensions_Corners}

\begin{sidewaystable}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
	\hline
	Fuel (\# of tests)      &   Wall Type   & Max. Height Left (m)	 	& Area Left (m$^2$)				&  Max. Height Right (m)        & Area (m$^2$)  				\\ \hline \hline
		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.15 (20~\%)  & 0.061 $\pm$ 0.028 (46~\%) 	&  0.78 $\pm$ 0.17 (22~\%) 	 	& 0.061 $\pm$ 0.028 (46~\%)  	\\
		Gasoline (10)       &   Open    	& 0.47	$\pm$ 0.26 (55~\%)  & 0.027 $\pm$ 0.019 (70~\%) 	&  0.45 $\pm$ 0.31 (69~\%)  	& 0.019 $\pm$ 0.011 (58~\%)\\
		PUF (3)       		&   Open 		& 0.32	$\pm$ 0.13 (41~\%)  & 0.056 $\pm$ 0.034 (61~\%) 	&  0.36 $\pm$ 0.091 (25~\%)  	& 0.071 $\pm$ 0.023 (32~\%)\\
	\hline
	\end{tabular}
	\caption[Comparison of corner fire pattern height and area for the three types of burners]{Comparison of corner fire pattern height and area for the three types of burners. Values presented with 95~\% confidence limits.}
	\label{tab:Fire_Pattern_Dimensions_Corners}
\end{sidewaystable}

@@

Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fueled burner in the corner position with walls of open back construction.

@@

	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner with walls of open construction.}
	\label{Gas_Corner}
\end{figure}

@@

Figure~\ref{PUF_Corner} shows a comparison of three fire patterns generated by the polyurethane foam fueled burner in the corner position with walls of open back construction. Only three replicates could be conducted due to the limits on the foam supply that was sourced from the same purchase.

\begin{figure}[p]
	\includegraphics[width=1.7in]{../Figures/GBPUF11_Corner}
	\includegraphics[width=1.7in]{../Figures/GBPUF12_Corner}
	\includegraphics[width=1.7in]{../Figures/GBPUF13_Corner} \\

	\caption[Photographs of the fire patterns from three replicate polyurethane foam burner experiments positioned in a corner]{Photographs of the fire patterns from three replicate polyurethane foam fueled burner experiments positioned in a corner with walls of open construction.}
	\label{PUF_Corner}
\end{figure}
